Supplementary Appendix

### 2023-06-16 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd

---
output:
  word_document: default
  html_document: default
---
# Reply to the Reviewer #2

__Other changes__
1. Subscript (j,k) changed to (j,i). k is already used in spline notation. 
2. Title of figures. Explicitly add what low, middle, and high mean so the reader do not need to go back to the main text to search the definitions.

@@

<br>

<span style = "color: blue;">General Comments</span>

<span style = "color: blue;">To some extent, this research is related to studies that examine the “value” of forecasting models by assessing their measure of inaccuracy. Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the “value” of certain econometric techniques?
</span>  
Reply: Very good point. What makes this study differ from previous studies is the model “value” is not measured by the accuracy of parameter estimates, but the ultimate economic return. We agree it is a good idea to add more review of previous studies and highlight our difference. 
More discussion, literature review, is added on page xx, lines xxx.

<span style = "color: blue;">One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching. Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p. 10, line 294 that represent the negative environmental externalities. The authors should clarify early on that “economically optimal” means “privately optimal” rather than “socially optimal.”</span>  
Reply: Thank you for the suggestion of clarifying the definition of "economically optimal". We added some explicit description in the introduction section (page xx, lines xxx) that the economical optimization in this study only includes farmers' private profit, and environmental externalities are not considered in this study.

<span style = "color: blue;">It strikes me as odd that, even with a minor clause on line 207 of p. 10, there is no real discussion of the corn price or nitrogen price in the methods section. What are the summary statistics and/or assumptions about p and w? What is the underlying intuition regarding the dependence of the relative performance of GWRR/GWRT to the corn-to-nitrogen price ratio (though this is partially explained in the paragraph on pages 15-16)? Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>  
Reply: Thank you for bringing up this point regarding the discussion of price information in the study. We have included a brief discussion of the historical corn and nitrogen prices in the results section (page x, lines xxx), explaining the three ratios represented the historically low, middle, and high price ratio scenarios. Additionally, we have created an appendix in the supplementary material (Appendix I: Historical Corn and Nitrogen Prices) to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data. We also apologize for the typos of the price ratios 4.16, 5.44 and 10.35 in the previous version manuscript. The correct price ratios should be 5.44, 6.56, and 7.67. They were all corrected in the revised manuscript.
For the underlying intuition regarding the dependence of relative performance of GWRR/GWRT to the nitrogen-corn price ratio, as explained in the paragraphs on pages 15-16 of the original manuscript, we believe the main difference arises from the specification of the $N^2$ coefficient in the models The GWRR model allows for a varying coefficient on $N^2$, leading to a wider range of estimated EONRs, while the GWRT model restricts the $N^2$ to be constant, leading to a narrower range of estimated EONRs. At higher nitrogen-corn price ratio, where nitrogen is relatively more expensive, the true range of EONRs should be larger, and therefore the economic penalty of GWRR's over-estimation of EONR range will be smaller. On the opposite, at lower nitrogen-corn price ratio, the true EONR range will be smaller, and the GWRT's under-estimation of EONR range is less of an issue. We believe this explanation adequately addresses the intuition behind the observed results. However, if the reviewer feels that further clarification is needed, please let us know, and we will be more than willing to provide additional discussion to enhance the understanding of our findings.

### 2023-06-16 Writing/manuscript_gwr.rmd
price history; a few other edits
finalize appendix; clear the folder;

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data. They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of VRA over URA reported in previous studies (cite). @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis, unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.

@@

The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial. In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions. But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR.

The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form. We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial. Both of them assumed a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient. It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study. As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values. Finally, we also evaluate their relative performances compared to URA based on shape-constrained additive model approach.

@@

In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates. When using the historical average corn and N prices (past 20 years, 2002-2021), the means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios. The comparative advantage of GWRR and GWRT varies significantly depending on nitrogen-corn price ratio. Specifically, GWRR performs better as the price ratio increases (as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWRT. At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA. However, when the price ratio increases to $6.56$, the median benefit of GWRR is `r round(mean_data_value[type == "GWRR" & pLabel == "6.56", pi_diff], digits = 2)`. At high price ratio of 7.67, the median benefit increases to `r round(mean_data_value[type == "GWRR" & pLabel == "7.67", pi_diff], digits = 2)`. On the other hand, the median benefit of VRA based on GWRT when the price ratio is low of 5.44 is `r round(mean_data_value[type == "GWRT" & pLabel == "5.44", pi_diff], digits = 2)`, but the benefit reduces to `r round(mean_data_value[type == "GWRT" & pLabel == "6.56", pi_diff], digits = 2)` when the price ratio is 6.56, and `r round(mean_data_value[type == "GWRT" & pLabel == "7.67", pi_diff], digits = 2)` when 7.67.

>>>>

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data. They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies (cite). @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis, unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.

@@

The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application (VRA), not just @trevisan2021spatial. In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions. But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR.

The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (or "variable rate application", VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form. We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial. Both of them assumed a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient. It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study. As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values. Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach. It should be noted that the economical optimization in this study only includes farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.

@@

In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates. When using the historical average corn and N prices (of the past two decades from 2002 to 2022), the means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg). Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service (NASS, 2022) and DTN Retail Fertilizer Trends (DTN, 2022), and were transformed into monthly data. The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$). Further information regarding the collection, calculation, and summary statistics of the price data can be found in Appendix I: Historical Corn and Nitrogen Prices in the supplementary material.

The comparative advantage of GWRR and GWRT varies significantly depending on nitrogen-corn price ratio. Specifically, GWRR performs better as the price ratio increases (that is, as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWRT. At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA. However, when the price ratio increases to $6.56$, the median benefit of GWRR is `r round(mean_data_value[type == "GWRR" & pLabel == "6.56", pi_diff], digits = 2)`. At high price ratio of 7.67, the median benefit increases to `r round(mean_data_value[type == "GWRR" & pLabel == "7.67", pi_diff], digits = 2)`. On the other hand, the median benefit of VRA based on GWRT when the price ratio is low of 5.44 is `r round(mean_data_value[type == "GWRT" & pLabel == "5.44", pi_diff], digits = 2)`, but the benefit reduces to `r round(mean_data_value[type == "GWRT" & pLabel == "6.56", pi_diff], digits = 2)` when the price ratio is 6.56, and `r round(mean_data_value[type == "GWRT" & pLabel == "7.67", pi_diff], digits = 2)` when 7.67.

### 2023-06-16 Writing/supplementary_appendix.rmd
finalize appendix; clear the folder;

```{r include = FALSE}
kernel_ls <- c("gaussian", "bisquare", "exponential", "tricube", "boxcar")

@@

# Appendix: Results with Alternative Kernel Functions {-}

@@

```{r, fig.id = "kernel", fig.cap = "List of Kernel functions"}
knitr::include_graphics("kernel_function_list.png")
```

@@

Figures A\@ref(fig:value-kernel-bs) through A\@ref(fig:value-kernel-boxcar) show the distribution of the true economic value of GWR using four different kernels: Bi-square, Exponential, Tri-cube, and Boxcar.

@@

```{r, fig.id = "value-kernel-bs", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Bi-square kernel", fig.height = 3.5}
gg_appendix$g_value[[2]]
```

```{r, fig.id = "value-kernel-exponential", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Exponential kernel", fig.height = 3.5}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "value-kernel-tricube", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Tri-cube kernel", fig.height = 3.5}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "value-kernel-boxcar", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Boxcar kernel", fig.height = 3.5}
gg_appendix$g_value[[5]]
```

@@

Figures A\@ref(fig:bias-kernel-bs) through A\@ref(fig:bias-kernel-boxcar) show the distribution of the bias in the estimated economic value of GWR. Similar to the findings from using the Gaussian kernel presnted in Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices. Also, the GWRT demonstrates smaller over-estimation at low price ratios compared to GWRR, while the over-estimation increases as price ratio rises. The presence of a similar fat tail in the GWRT bias distribution is also evident. The magnitudes of the estimation bias vary across kernel function choices, but the differences are not substantial and do not affect qualitatively our conclusions drawn in the main text.

```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Bi-square kernel", fig.height = 3.5}
gg_appendix$g_bias[[2]]
```

```{r, fig.id = "bias-kernel-exponential", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Exponential kernel", fig.height = 3.5}
gg_appendix$g_bias[[3]]
```

```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Tri-cube kernel", fig.height = 3.5}
gg_appendix$g_bias[[4]]
```

```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Boxcar kernel", fig.height = 3.5}
gg_appendix$g_bias[[5]]
```

>>>>

```{r include = FALSE}
kernel_ls <- c("gaussian", "exponential", "boxcar", "bisquare", "tricube")

@@

# Appendix I: Historical Corn and Nitrogen Prices {-}

Figure A\@ref(fig:price) illustrates the historical prices of corn ($p$) and nitrogen fertilizer ($w$), along with the corresponding nitrogen-corn price ratios, during the two-decade period from 2002 to 2022.

```{r, fig.id = "price", fig.cap = "Historical monthly variations in corn price, nitrogen fertilizer price, and the corresponding nitrogen-corn price ratio, 2002-2022"}
knitr::include_graphics("price_ratio_history.png")
```

Corn prices were sourced from the USDA National Agricultural Statistics Service [@NASS2022] in monthly frequency from 2002 to 2022. As shown in the top panel of Figure A1, the corn prices fluctuated between \$0.07/kg and \$0.30/kg, with an average of $0.15/kg.

Nitrogen prices were collected from two sources. The USDA National Agricultural Statistics Service provided yearly nitrogen fertilizer prices for the period 2002 to 2014. The DTN Retail Fertilizer Trends [@DTN2022] provided weekly nitrogen fertilizer prices from 2015 to 2022. To align with the monthly corn price data, the nitrogen price data from both sources were combined and converted into monthly data. Three most commonly used nitrogen fertilizer types were included: Liquid urea-ammonium nitrate with 28 percent nitrogen (UAN28), Liquid urea-ammonium nitrate with 32 percent nitrogen (UAN32), and anhydrous ammonia (ANHYD). All prices were all converted to the per kilogram (kg) of nitrogen basis. As shown in the middle panel of Figure A1, the nitrogen prices ranged from \$0.34/kg to \$2.37/kg, with an average of \$0.98/kg.

The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$), and the results were shown in the bottom panel of Figure A1. This study took the values at the 25th, 50th, and 75th percentiles of the historical monthly price ratios (pooled over the three types of nitrogen fertilizer) from 2002 to 2022. These three values were used to represent the low (5.44), middle (6.56), and high (7.67) price ratio scenarios. For consistency purposes, in the profitability calculations the corn price was selected at approximately the Spring 2022 price of \$0.28/kg. Consequently, the corresponding nitrogen prices for the three price ratio scenarios were approximately 5.44×0.28 = \$1.52/kg, 6.56×0.28 = \$1.84/kg, and 10.35×0.28 = \$2.15/kg. It is important to note that when different corn prices are used, the resulting profits of GWR will vary accordingly, but the variation will be proportional to the result of selected corn price and does not qualitatively alter the final conclusions.

# Appendix II: Results with Alternative Kernel Functions {-}

@@

```{r, fig.id = "kernel", fig.cap = "List of Kernel functions for GWR modeling. In the graphs of kernel function curves, the y-axis is the kernel weight, and the x-axis is the ratio of ($d_{ab}/h$). "}
knitr::include_graphics("kernel_function_list.png")
```

@@

Figures A\@ref(fig:value-kernel-exp) through A\@ref(fig:value-kernel-tricube) show the distribution of the true economic value of GWR using four different kernels: Exponential, Boxcar, Bi-square, and Tri-cube.

@@

```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
gg_appendix$g_value[[2]]
```

```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
gg_appendix$g_value[[5]]
```

@@

Figures A\@ref(fig:bias-kernel-exp) through A\@ref(fig:bias-kernel-tricube) show the distribution of the bias in the estimated economic value of GWR. Similar to the findings from using the Gaussian kernel presented in Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices. Also, the GWRT demonstrates smaller over-estimation at low price ratios compared to GWRR, while the over-estimation increases as price ratio rises. The presence of a similar fat tail in the GWRT bias distribution is also evident. The magnitudes of the estimation bias vary across kernel function choices, but the differences are not substantial and do not affect qualitatively our conclusions drawn in the main text.

```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
gg_appendix$g_bias[[2]]
```

```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
gg_appendix$g_value[[5]]
```
